---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(stringr)

date <- "3/29/2018"
vendor <- "Pizza Capri"
title <- "Conference @ Github"
file_title <- "Lightning Talk Schedule"
short_title_n = 2
speaker <- "Spring 2018 MACSS Student Conference"
department <- "A Debut of the 2016 Cohort's Master Thesis Research"
university <- "Lightning Talk Schedule"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computational Social Science Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3>
  <a href="https://docs.google.com/spreadsheets/d/16-5wUB0xmpvMVjqaQThD5TUMvufncGi3ztG1cnPE3p4/edit#gid=0" >`r university`</a></h3>
<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header>
  <a href="https://github.com/uchicago-computation-workshop/2018_spring_conference" >`r title`</a>
</h2>

<br>
</div>

<p class=footertext2>

**Abstract:** The 2018 MACSS Student Conference will feature research from the 2016 Cohort in the [Masters of Computational Social Science](https://macss.uchicago.edu) program at the University of Chicago. Thesis research comes from a variety of fields in the social sciences including but not limited to Sociology, Political Science, Psychology, Criminology, Economics, and Comparative Human Development using a variety of computational methods such as Spatial Regression, Natural Language Processing, Web Scraping, and Machine Learning.
<p class=footertext2>
<br>

<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 5:00pm - 7:00pm </h4>
<h4 class=pfblock-header3> Social Science Research Building 122 </h4>

<br>

<p class=pfblock-header3>A dinner reception will follow provided by `r vendor`.</p>

<br><br>

<p class=footertext2>

**Logistical Details for MACSS Presenters:** Talks will be in [Ignite-style](http://www.ignitetalks.io/), which means that **by noon on Thursday, May ,** all 2nd year students will send a PDF with 20 slides to *both* James Evans and Joshua Mausolf **and update the title of their talk** on the spreadsheet linked below. The slides will be spliced together and auto-advance every 15 seconds. We will add a transition slide between every presentation (15 seconds) for a literally jam-packed evening of Computational Social Science. The [order of speakers](https://docs.google.com/spreadsheets/d/16-5wUB0xmpvMVjqaQThD5TUMvufncGi3ztG1cnPE3p4/edit?usp=sharing) is detailed on the linked page.


</p>




<br><br>

---

<p class=footertext> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> meets each Thursday from 11 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome.</p>

<p class=footertext>This special session is required for all second year MACSS students (must present), and all first years (must attend). If a presenter needs to shift times in the program, please find someone in the program to switch (then swap on the sheet).</p>

<p class=footertext> As a reminder, all students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="https://github.com/uchicago-computation-workshop/2018_spring_conference/issues"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a> Further instructions are documented in the Computational Social Science Workshop's <a href="https://github.com/uchicago-computation-workshop/README"> README on Github.
</a></p>
